---
title: "**The Cereal Dataset SLR Exercise**"
output: html_notebook
---

##Quick Intro
I am going to try to standardize the analysis and force myself to a methodology.<br \> Will be trying to follow these points:

  1. Set the working directory to where the data is.
  1. Data preprocessing.
    - Choosing the right set of variables (in this case *rating* of a cereal and *sugar* content).
    - Making sure there are no missing values.
    - Cheking the type of values contained in the variables.
    - Splitting dataset into training and test data sets.
  1. Fitting SLR to *training set*.
  1. Predicting *test set* results.
  1. Visualizing *training set* results.

## Set WD

```{r}
setwd("D:/Dropbox/Clases/Udemy/Machine Learning A-Z/machinelearning/Course Notes/Exercises on my own/SLR")
```

## Data Preprocessing

### Setting up the dataset in a suitable format

Data for this exercise was aquired online in a space separated .csv document. There are no missing values and the variables of interest for this analysis are numerical.

```{r}

# Reading data into a table format WITHOUT a header.
dataset <- read.table('cereal.csv', sep = '', header = TRUE)

# Adding variable names as headers to the dataset
#names(dataset) <- c('name', 'mfr', 'type', 'calories', 'protein', 'fat', 'sodium', 'fiber', 'carbo', 'sugars', 'shelf', 'potass', 'vitamins', 'weight', 'cups')

#Visualizing the first 10 entries.
head(dataset)
```

### Selecting the variables `sugars` y `rating`

Only 2 variables are going to be used in this analysis, so a new dataset is generated containing the name of the product plus the variables of interest.

```{r}
vars <- c("name", "sugars", "rating")

datasetlm <- dataset[vars]

head(datasetlm)
```

### Splitting the dataset into `training` and `test`.

We will go with a split ratio of 70% for the training set and 30% for the test set.<br \>
It is improtant to remember that `rating` will be the dependent variable and `sugar` the independent one.

```{r}
library(caTools)
set.seed(123)

split <- sample.split(datasetlm$rating, SplitRatio = 2/3)
training_set <- subset(datasetlm, split == TRUE)
test_set <- subset(datasetlm, split == FALSE)

```

## Fitting SLR to `training_set`

```{r}
regressor <- lm(formula = rating ~ sugars,
                data = training_set)
summary(regressor)
```

The `summary` of the `regressor` on the variables`rating` as dependent and `sugars` as independet reports a $p = 1.15^{-15}$, therefore these variables are **strongly related**.

## Predicting `test_set` results

```{r}
y_pred <- predict(regressor, newdata = test_set)
```

## Visualization

### Training_set
```{r}
library(ggplot2)

ggplot() +
  geom_point(aes(x = training_set$sugars, y = training_set$rating),
             colour = 'red') +
  geom_line(aes(x = training_set$sugars, y = predict(regressor, newdata = training_set)),
            colour = 'blue') +
  ggtitle('Nutritional Rating vs Sugars (training_set)') +
  xlab('Amount of Sugar') +
  ylab('Nut.Rating')
```

### Test_set

```{r}
library(ggplot2)

ggplot() +
  geom_point(aes(x = test_set$sugars, y = test_set$rating),
             colour = 'red') +
  geom_line(aes(x = training_set$sugars, y = predict(regressor, newdata = training_set)),
            colour = 'blue') +
  ggtitle('Nutritional Rating vs Sugars (test_set)') +
  xlab('Sugars') +
  ylab('Nut.Rating')
```
