---
title: "Principal Component Analysis (PCA)"
output: html_notebook
---
<br \>
<br \>
PCA seeks to explain the correlation structure of a set of predictor variables using a smaller set of linear combinations (components) of these variables.


## Implementation in R

To run a PCA in R it is important to have the packages `caret` and `e1071` installed.

### Creating the Variable PCA

It will later be used to transform original dataset with the new extracted features.
```{r}
library(caret)
library(e1071)
#pca <- preProcess()
```

##Importing the dataet

```{r}
dataset = read.csv('Wine.csv')
```

##Spliting `dataset` into Training and Test sets

```{r}
library(caTools)
set.seed(123)
split <- sample.split(dataset$Customer_Segment, SplitRatio = 0.8)
training_set <- subset(dataset, split == TRUE)
test_set <- subset(dataset, split == FALSE)
```

##Feature Scaling
```{r}
training_set[-14] <- scale(training_set[-14])
test_set[-14] <- scale(test_set[-14])
```

###Applying PCA to the data
```{r}
pca <- preProcess(x <- training_set[-14], method = "pca", pcaComp = 2)
training_set <- predict(pca, training_set)
training_set <- training_set[c(2,3,1)] #puting the column of target variable on the far right of the dataset.

test_set <- predict(pca, test_set)
test_set <- test_set[c(2,3,1)] #puting the column of target variable on the far right of the dataset.
```

###Bulding a Classification Model

From this point on, we can run any model wanted for data prediction. In this case we will use a Support Vector Machine.

```{r}
library(e1071)
classifier <- svm(formula = Customer_Segment ~ .,
                  data = training_set,
                  type = "C-classification",
                  kernel = "linear")
```

####Predicting `test_set` results.
```{r}
y_pred <- predict(classifier, newdata = test_set[-3])
```

####Making Confusion Matrix
```{r}
cm <- table(test_set[,3], y_pred)
cm
```

###Visualising the Training set results

```{r}
library(ElemStatLearn)
set = training_set
X1 = seq(min(set[, 1]) - 1, max(set[, 1]) + 1, by = 0.01)
X2 = seq(min(set[, 2]) - 1, max(set[, 2]) + 1, by = 0.01)
grid_set = expand.grid(X1, X2)
colnames(grid_set) = c('PC1', 'PC2')
y_grid = predict(classifier, newdata = grid_set)
plot(set[, -3], main = 'SVM (Training Set)',
     xlab = 'PC1', ylab = 'PC2',
     xlim = range(X1), ylim = range(X2))
contour(X1, X2, matrix(as.numeric(y_grid), length(X1), length(X2)), add = TRUE)
points(grid_set, pch = '.', col = ifelse(y_grid == 2, 'deepskyblue', ifelse(y_grid == 1, 'springgreen3', 'tomato')))
points(set, pch = 21, bg = ifelse(set[, 3] == 2, 'blue3', ifelse(set[, 3] == 1, 'green4', 'red3')))
```


###Visualising the Test Set Results

```{r}
library(ElemStatLearn)
set = test_set
X1 = seq(min(set[, 1]) - 1, max(set[, 1]) + 1, by = 0.01)
X2 = seq(min(set[, 2]) - 1, max(set[, 2]) + 1, by = 0.01)
grid_set = expand.grid(X1, X2)
colnames(grid_set) = c('PC1', 'PC2')
y_grid = predict(classifier, newdata = grid_set)
plot(set[, -3], main = 'SVM (Test Set)',
     xlab = 'PC1', ylab = 'PC2',
     xlim = range(X1), ylim = range(X2))
contour(X1, X2, matrix(as.numeric(y_grid), length(X1), length(X2)), add = TRUE)
points(grid_set, pch = '.', col = ifelse(y_grid == 2, 'deepskyblue', ifelse(y_grid == 1, 'springgreen3', 'tomato')))
points(set, pch = 21, bg = ifelse(set[, 3] == 2, 'blue3', ifelse(set[, 3] == 1, 'green4', 'red3')))
```