---
title: "Multiple Linear Regression Implementation in R"
output: html_notebook
---


### Setting the WD

```{r}
setwd("D:/Dropbox/Clases/Udemy/Machine Learning A-Z/Part 2 - Regression/Section 5 - Multiple Linear Regression")
```

### Data Preprocessing

We will be using the same data preprocessing template used in previous excercises:
A few things to remember:

  - Shince there is a variable with categorical values it has to be encoded.
  - There is no need to do feature scaling since the function used in R will take care of that already.
```{r}
# Data Preprocessing template

# Importing the dataset
dataset = read.csv('50_Startups.csv')
# dataset = dataset[, 2:3]

#Encoding Categorical Data, this is important because a regression model cannot work with categorical values.
dataset$State <- factor(dataset$State,
                        levels = c('New York', 'California', 'Florida'),
                        labels = c(1, 2, 3))

# Splitting the dataset into the Training set and Test set
# install.packages('caTools')
library(caTools)
set.seed(123)
split = sample.split(dataset$Profit, SplitRatio = 0.8)
training_set = subset(dataset, split == TRUE)
test_set = subset(dataset, split == FALSE)

# Feature Scaling
# training_set[, 2:3] = scale(training_set[, 2:3])
# test_set[, 2:3] = scale(test_set[, 2:3])
```

### Fitting Multiple Linear Regression to the Training Set

First a `regressor` has to be generated to fit the training set, later on it will be used in the process.

```{r}
#regressor <- lm(formula = Profit ~ R.D.Spend + Administration + Marketing.Spend + State)

regressor <- lm(formula = Profit ~ . , #Using the . tells R to add all the independent variables.
                data = training_set) 
```

### Generating the `regressor`

Taking a look at the `regressor` just generated can be done with the comand `summary()`, this will start showing us important imformation regarding the influence independent variables might have on the dependent one.
```{r}
summary(regressor)
```

Some important things to notice:

  - R has already taken care of the *dummy variable* creation for `State`.
  - R has also staid out of the **dummy variable trap** and kept one of the tree generated out of the calculations.
  
According to the resutls from the `regressor` a very important conclussion can be drawn: `R.D.Spend` is the only variable, out of all the independent ones, that has a strong statistical impact on the independent variable `Profit`.

